A systematic search for transiting planets in the \KT\ data

### 2015-02-15 ms.tex
performance section tweaks

To test the performance and detection efficiency of our method, we conducted a
suite of \dfmtodo{XXXX} injection and recovery tests, five tests per
target star.
For each test, we inject the signal from a realistic planetary system into the
raw aperture photometry of a random target and run the resulting injected light curve
through the full pipeline (except the manual vetting).
If the search returns a planet candidate---passing all of the same cuts as we
apply in the main search---with period and reference transit time within
\dfmtodo{HOWMANY~days} of the injected signal, we count that injection as recovered.
The detection efficiency of the search is given approximately by the fraction
of recovered injections as a function of the relevant parameters.

To generate the synthetic signals, we use the following procedure:
\begin{enumerate}

{\item Draw the number of transiting planets based on the observed
multiplicity distribution of KOIs (\dfmtodo{CITE}).}

{\item Sample---from the distributions listed in
\tab{dist}---limb darkening parameters and, for each planet, an orbital
period, phase, radius ratio, impact parameter, eccentricity, and argument of
periapsis.}

{\item Based on the chosen physical parameters, simulate the light curve,
taking limb darkening and integration time into account \citep{ma,
kipping-int}, and multiply it into the raw aperture photometry.}

\end{enumerate}
We then process these light curves using exactly the pipeline that we use for
the light curves without injections.
Finally, we test for recovery after applying the cuts in signal-to-noise and
period.
We should, of course, also process the results of the injection tests by hand
to ensure that our measurements of detection efficiency aren't biased by this
step but, since we chose to limit our sample to very high signal-to-noise
candidates, it seems unlikely that our hand vetting removed any true transit
signals.
Any estimates of the false alarm rate will, however, be affected by this
negligence but we leave a treatment of this for future discussion.

\Fig{completeness} shows the fraction of recovered signals as a function of
the physical parameters of the injection and the magnitude of the star.
As expected, the shallower transits at longer periods are recovered less
robustly.
It is worth noting that this figure is a two-dimensional projection (or
marginalization) of a higher dimensional measurement.
For example, this completeness map is conditioned on our assumptions about
the eccentricity distribution of planets and it is marginalized over the
distribution of stellar parameters.
It is possible to relax this assumption and apply different distributions by
re-weighting the simulations used to generate this figure.
Therefore, alongside this \paper, we publish the full list of injection
simulations\footnote{SOMEURL} to be used for population inference (occurrence
rate measurements).
In \fig{completeness}, we also show the detection efficiency---marginalized
over the same range of periods---as a function of stellar magnitude in the
\kepler\ bandpass as reported in the EPIC.

>>>>

To test the performance and detection efficiency of our method, we conducted a
suite of injection and recovery tests, five per
star for all 21,703 target stars.
For each test, we inject the signal from a realistic planetary system into the
raw aperture photometry of a random target and run the resulting injected light curve
through the full pipeline (except the manual vetting).
If the search returns a planet candidate---passing all of the same cuts as we
apply in the main search (except the manual vetting)---with period and reference transit time within
\dfmtodo{HOWMANY~days} of the injected signal, we count that injection as recovered.
The detection efficiency of the search is given approximately by the fraction
of recovered injections as a function of the relevant parameters.

To generate the synthetic signals, we use the following procedure:
\begin{enumerate}
{\item Draw the number of transiting planets based on the observed
multiplicity distribution of KOIs (\dfmtodo{CITE}).}
{\item Sample---from the distributions listed in
\tab{dist}---limb darkening parameters and, for each planet, an orbital
period, phase, radius ratio, impact parameter, eccentricity, and argument of
periapsis.}
{\item Based on the chosen physical parameters, simulate the light curve,
taking limb darkening and integration time into account \citep{ma,
kipping-int}, and multiply it into the raw aperture photometry.}
\end{enumerate}
We then process these light curves using exactly the pipeline that we use for
the light curves without injections.
Finally, we test for recovery after applying the cuts in signal-to-noise and
period.
We should, of course, also vet the results of the injection tests by hand
to ensure that our measurements of detection efficiency aren't biased by the
hand-vetting
step but, since we chose to limit our sample to very high signal-to-noise
candidates, it seems unlikely that our hand vetting removed any true transit
signals.
Any estimates of the false alarm rate will, however, be affected by this
negligence but we leave a treatment of this for future work.

\Fig{completeness} shows the fraction of recovered signals as a function of
the physical parameters of the injection and the magnitude of the star.
As expected, the shallower transits at longer periods are recovered less
robustly.
It is worth noting that this figure is a two-dimensional projection (or
marginalization) of a higher dimensional measurement.
For example, this completeness map is conditioned on our assumptions about
the eccentricity distribution of planets and it is marginalized over the
empirical distribution of stellar parameters.
It is possible to relax this assumption and apply different distributions by
re-weighting the simulations used to generate this figure.
Therefore, alongside this \paper, we publish the full list of injection
simulations\footnote{SOMEURL} to be used for population inference (occurrence
rate measurements).
In \fig{completeness}, we also show the detection efficiency---marginalized
over the same range of periods---as a function of stellar magnitude in the
\kepler\ bandpass as reported in the EPIC (\dfmtodo{CITATION NEEDED?}).
